Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/testing.tex
Wordsmithing in 'mistakes' paragraph

There are three common mistakes in specifications, aside from self-consistency that is already checked, that have been observed: vacuity, under-specification, and missed corner cases.
Vacuity is a common pitfall with implication when the left hand side is always false making the implication true. 
Under-specification is very challenging because verification is not able to prove anything (or it can prove everything in the case of existential properties) so nothing is actually known after verification except that the system is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is especially hard here because there is no direct way to provide test input and check test output.

>>>>

We have observed three common types of mistakes in specifications (aside from self-consistency, which is
already checked): vacuity, under-specification, and missed corner cases.
Vacuity is a common pitfall with implication when the left hand side is always false, making the implication true. 
Under-specification is very challenging, as a verifier in the face of under-specification is not able to prove anything (or it can prove everything in the case of existential properties), so nothing is actually known after verification except that the system is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is an especially difficult challenge here because there is no direct way to provide test input and check test output.
